
\documentclass[margin,line]{res}
\usepackage[colorlinks=true, urlcolor=black, linkcolor=red]{hyperref}
\usepackage{etaremune}

\newcommand\tab[1][1cm]{\hspace*{#1}}
\urlstyle{same}

\oddsidemargin -.5in
\evensidemargin -.5in
\textwidth=6.0in
\itemsep=0in
\parsep=0in

\newenvironment{list1}{
  \begin{list}{\ding{113}}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0.17in}}}{\end{list}}
\newenvironment{list2}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0.2in}}}{\end{list}}


\begin{document}
\begin{flushleft}
		\huge \textbf{Kristin M. Eccles}
		\hfill {\LARGE \textbf{Curriculum Vitae}}\\
\end{flushleft}

\begin{resume}

\section{\sc Contact Information}
\vspace{.05in}
\begin{tabular}{@{}p{3.2in}p{2.5in}}
Exposure and Biomonitoring Division & {\it E-mail:}  kristin.eccles@hc-sc.gc.ca\\
Health Canada &{\it Website:} https://kristineccles.wordpress.com  \\
251 Sir Frederick Banting Driveway&{\it GitHub:} https://github.com/kristineccles \\
Sir Frederick Banting Building& {\it ORCID}: 0000-0002-6629-430X\\
Ottawa, ON, K1A 0K9

\end{tabular}

\vspace*{.1in}
\section{\sc Highlights}
32 peer-reviewed publications (12 as first author, 1 as senior author)
\\
604 citations; h index = 15 and i10 index = 17
\\
Research Expertise: Mixtures, Exposome, Biomarkers, NAMs, AEP-AOP

\vspace*{.1in}
\section{\sc Current\\Position}
{\bf  Research Scientist} \hfill {\bf July 2023 - Present}\\
Principle Investigator, Computational Toxicology Research Group\\
Exposure and Biomonitoring Division, Health Canada\\
Ottawa, Ontario, Canada

%%%%%%% Education %%%%%%%
\vspace*{.1in}
\section{\sc Education}

\textbf{Ph.D., Biology with Specialization in Chemical and Environmental Toxicology} \hfill {\bf 2019}\\
Department of Biology, University of Ottawa, Ottawa, Canada \\
Adviser: Laurie Chan, Ph.D.

\textbf{M.Sc., Geography}  \hfill {\bf 2014}\\
Department of Geography, University of Calgary, Calgary, Canada\\
Advisers:  Stefania Bertazzon, Ph.D. and Sylvia Checkley, Ph.D.

\textbf{Honours B.A., Health Studies, Minors: Geography and Earth Science }\hfill {\bf 2012}\\
McMaster University, Hamilton, Canada\\
Adviser: John Eyles, Ph.D.

%%%%%%% Appointments %%%%%%%
\vspace*{.1in}
\section{\sc Professional Appointment/ Employment}

{\bf  Postdoctoral Research Fellow} \hfill {\bf Nov 2020 - May 2023}\\
National Institute of Environmental Health Science, Division of Translational Toxicology,\\
Durham, North Carolina, USA\\
Advisers: Cynthia Rider, Ph.D and Kyle Messier, Ph.D.

{\bf Postdoctoral Fellowship} \hfill {\bf Aug 2019 - Oct 2020}\\
Department of Geography, Geomatics and Environment, University of Toronto, Mississauga, Canada\\
Advisers: Igor Lehnherr, Ph.D. and Trevor Porter, Ph.D.

%%%%%%% Publications %%%%%%%
\section{\sc Peer-reviewed Publications}

%\begin{etaremune}[start=26]
%\textbf{Eccles, K.M.}, Yee, S., Chan, H.M. (2025). A Meta-Analysis Of Methylmercury:Total Mercury Ratio In Traditional Foods In Canada And Implications For Risk Assessment. \textit{Under Review}.

\textbf{Eccles, K.M.}, Gaston, K., Green, E.M., Waidyanatha, S., Stuffler, B., Harris, S.F., Rider, C.V., Meadlock Kakaley, E. (2026). Challenging Additivity: Comparing Predicted and Observed AhR Activity of Polycyclic Aromatic Compound (PAC) Mixtures Containing Active and Inactive Constituents.\textit{Environmental Science \& Technology}.\url{https://doi.org/10.1021/acs.est.5c11914}\\

Blais, A., Loan, A., Cho, E., Woodtke, A., Moteshareie, H., Bradford, L. M., Zhang, G., Pelletier, G., Navarro, M., Meier, J., Nong, A., Aranda-Rodriguez, R., \textbf{Eccles, K.M.}, Prescott, D., Tayabali, A. (2026). PFOS and PFOA Exposure Induces Liver Injury and Sex-Dependent Immune Effects in C57BL/6 Mice. \textit{iScience}. \url{https://doi.org/10.1016/j.isci.2026.114693}\\

Lee, H., Curry, J., Stead, J.D.H., Williams, A., Atlas, E., \textbf{Eccles, K.M.}, Mennigen, J.A., Yauk, C., O'Brien, J.M. (2025). Acute toxicity, behaviour, metabolism and transcriptomic points of departure in embryo-larval zebrafish exposed to nine different PFAS. \textit{Journal of Hazardous Materials}, 140599.\url{https://doi.org/10.1016/j.jhazmat.2025.140599}

Heldman, S., \textbf{Eccles, K.M.}, Kassotis, C. (2025). Liquid Crystal Monomers and Their Mixtures Alter Nuclear Receptor Signaling and Promote Adipogenesis In Vitro. \textit{Endocrinology}, 166(11), bqaf143.\url{https://doi.org/10.1210/endocr/bqaf143}

Cho, E., Baird, S., \textbf{Eccles, K.M.} (2025). Smaller Scale, Same Impact: Replicating High-Throughputh Phenotypic Profiling in a Medium- Throughput Lab for Use in Chemical Risk Assessment. \textit{Archives of Toxicology}, 1-13. \url{https://doi.org/10.1007/s00204-025-04165-2}

Parham, F., \textbf{Eccles, K.M.}, Rider, C. V., Sakamuru, S., Xia, M., Huang, R., Tice, R.R., Dinse, G.E., DeVito M.J. (2025) Lessons learned from evaluating defined chemical mixtures in a high throughput estrogen receptor assay system.kfaf020. \url{https://doi.org/10.1093/toxsci/kfaf020}\\
\mbox{*}NIEHS paper of the month

\textbf{Eccles, K.M.}, Boutet, V. Branigan, M., Dyck, M., van Coeverden de Groot, P., Lougheed, S.C., Rutter A., Langlois V.S. (2024). Non-invasive biomonitoring of polar bear feces can be used to estimate concentrations of metals of concern in traditional food. \textit{PLoS one}, 19(6), e0305398. \url{https://doi.org/10.1371/journal.pone.0305398}

Stalwick, J., Somers, G., \textbf{Eccles K.M.}, Thomas, P.J., Cunada, C., Gurney, K. (2024). The Influence of Environmental Factors such as Snow and Fire on Spatial and Temporal Patterns of Polycyclic Aromatic Compounds in the Mackenzie.\textit{Environmental Pollution}, 123962. \url{https://doi.org/10.1016/j.envpol.2024.123962}

Cheney, C.L., \textbf{Eccles K.M.}, Lehnherr, I., Blais, J. M. (2024). Mercury deposition to lake sediments near historic gold mines in northern Canada. \textit{Environmental Pollution}, 123038. \url{https://doi.org/10.1016/j.envpol.2023.123038}

Vander Meulen, I. J., Schock, D. M., Akhter, F., Mundy, L. J., \textbf{Eccles K.M.}, Soos, C., Peru, K.M., McMartin, D.W., Headley, J.V. and Pauli, B.D. (2023). Site-specific spatiotemporal occurrence and molecular congener distributions of naphthenic acids in Athabasca oil sands wetlands of Alberta, Canada. \textit{Environmental Pollution}, 122061. \url{https://doi.org/10.1016/j.envpol.2023.122061}

Tommasi, F., Pagano, G., Oral, R., Thomas, P.J., \textbf{Eccles K.M.}, Tez, S., Toscanesi, M., Giarra,, A., Siciliano, A., Dipierro, N., Gjata, I,, Guida, M., Libralato, G., Lyons,D.M., Burić, P., Ines Kovačić, I.,  Trifuoggi, M. (2023). Topsoil pollution and multi-endpoint toxicity in the petrochemical area of Augusta-Priolo (eastern Sicily, Italy). \textit{Chemosphere}, 333, 138802. \url{https://doi.org/10.1016/j.chemosphere.2023.138802}

\textbf{Eccles K.M.}, Karmaus, A. L., Kleinstreuer, N. C., Parham, F., Rider, C. V., Wambaugh, J. F., Messier, K. P. (2023). A geospatial modeling approach to quantifying the risk of exposure to environmental chemical mixtures via a common molecular target. \textit{Science of The Total Environment}, 855, 158905. \url{https://doi.org/10.1016/j.scitotenv.2022.158905}\\
\mbox{*}NIEHS 2022 paper of the year

Boutet, V., Dominique, M., \textbf{Eccles, K.M.}, Branigan, M., Dyck, M., van Coeverden de Groot, P., Lougheed, S.C., Rutter A., Langlois V.S. An exploratory spatial contaminant assessment for polar bear (\textit{Ursus maritimus}) liver, fat, and muscle from Northern Canada. (2023). \textit{Environmental Pollution}, 316, 120663. \url{https://doi.org/10.1016/j.envpol.2022.120663}

Lowe, M.E., Akhtari, F., Potter, P.A., Fargo, D.C., Schmitt, C.P., Schurman, S.H., \textbf{Eccles, K.M.}, Motsinger-Reif, A., Hall, J.E., Messier, K.P. (2022). The skin is no barrier to mixtures: Air pollutant mixtures and reported
psoriasis or eczema in the Personalized Environment and Genes Study (PEGS). \textit{Journal of exposure science \& environmental epidemiology}.1-8. \url{https://doi.org/10.1038/s41370-022-00502-0}

Cui, Y., \textbf{Eccles K.M.}, Kwok, R.K., Joubert, B., Messier, K.P., Balshaw, D. (2022). Integrating Multiscale Geospatial Environmental Data into Large Population Health Studies: Challenges and Opportunities. \textit{Toxics}. 10(403). \url{https://doi.org/10.3390/toxics1007040}

 Thomas, P. J., Eickmeyer, D. C., \textbf{Eccles, K.M.}, Kimpe, L. E., Felzel, E., Brouwer, A., Blais, J. M. (2022). Paleotoxicity of petrogenic and pyrogenic hydrocarbon mixtures in sediment cores from the Athabasca oil sands region, Alberta (Canada). \textit{Environmental Pollution}, 292, 118271. \url{https://doi.org/10.1016/j.envpol.2021.118271}

\textbf{Eccles, K.M.}, Thomas, P. J., Chan, H. M. (2021). Spatial patterns of the exposure-response relationship between mercury and cortisol in the fur of river otter (\textit{Lontra canadensis}). \textit{Chemosphere}, 263, 127992. \url{https://doi.org/10.1016/j.chemosphere.2020.127992}

Thomas, P. J., Newell, E. E., \textbf{Eccles, K.M.}, Holloway, A. C., Idowu, I., Xia, Z., Quenneville, C. (2021). Co-exposures to trace elements and polycyclic aromatic compounds (PACs) impacts North American river otter (\textit{Lontra canadensis}) baculum. \textit{Chemosphere}, 265, 128920.\url{https://doi.org/10.1016/j.chemosphere.2020.128920}

\textbf{Eccles, K.M.}, Pauli, B.D., Chan, H.M. (2020). Geospatial analysis of complex metal exposures to biota in the Athabasca Oil Sands. \textit{PLoS one}, 15(9), e0239086. \url{https://doi.org/10.1371/journal.pone.0239086}

Galen, G., \textbf{Eccles, K.M}., MacMillian, M., Thomas, P. J., Chan, H.M., Poulain, A.J. (2020). The gut microbial community structure of the North American river otter (\textit{Lontra canadensis}) in the Alberta Oil Sands Region in Canada: relationship with local environmental variables and metal body burden.\textit{Environmental Toxicology and Chemistry}.39(12), 2516-2526. \url{https://doi.org/10.1002/etc.4876}

Etowa, J., Johnston, A., Jama, Z., \textbf{Eccles, K.M.}, Ashton, A. (2020). Mixed-method evaluation of a community-based postpartum support program: a study protocol. \textit{BMJ open}, 10(10), e036749. \url{https://doi.org/10.1136/bmjopen-2019-036749}

\textbf{Eccles, K.M.}, Majeed, H., Lehnherr, I., Porter, T. (2020). A continental and marine-influenced tree-ring mercury record in the Old Crow Flats, Yukon, Canada. \textit{ACS Earth and Space Chemistry}, 4(8), 1281-1290. \url{https://doi.org/10.1021/acsearthspacechem.0c00081.s001}

Cheney, C.L., \textbf{Eccles, K.M}., Kimpe, L.E., Blais, J.M. (2020). Determining the effects of past gold mining using a sediment palaeotoxicity model. \textit{Science of The Total Environment}, 718, 137308. \url{https://doi.org/10.1016/j.scitotenv.2020.137308}

\textbf{Eccles, K.M.}, Thomas, P. J., Chan, H. M. (2020). Relationships between mercury concentrations in fur and stomach contents of river otter (\textit{Lontra canadensis}) and mink (\textit{Neovison vison}) in northern Alberta Canada and their applications as proxies for environmental factors determining mercury bioavailability. \textit{Environmental Research}, 181, 108961. \url{https://doi.org/10.1016/j.envres.2019.108961}

\textbf{Eccles, K. M}., Pauli, B. D., Chan, H. M. (2019). The use of Geographic Information Systems (GIS) for spatial ecological risk assessments: An example from the Athabasca oil sands area in Canada. \textit{Environmental toxicology and chemistry}, 38(12): 2797–2810. \url{https://doi.org/10.1002/etc.4577}

\textbf{Eccles, K. M.}, Littlewood, E. S., Thomas, P. J., Chan, H. M. (2019). Distribution of organic and inorganic mercury across the pelts of Canadian river otter (\textit{Lontra canadensis}). \textit{Scientific reports}, 9(1), 3237. \url{https://doi.org/10.1038/s41598-019-39893-w}

 \textbf{Eccles, K. M.}, Thomas, P. J., Chan, H. M. (2017). Predictive meta-regressions relating mercury tissue concentrations of freshwater piscivorous mammals. \textit{Environmental Toxicology and Chemistry}, 36(6), 2377–2384. \url{http://doi.org/10.1002/etc.3775}

Thomas, P. J., \textbf{Eccles, K. M.}, Mundy, L. J. (2017). Spatial modelling of non-target exposure to anticoagulant rodenticides can inform mitigation options in two boreal predators inhabiting areas with intensive oil and gas development. \textit{Biological Conservation}, 212, 111-119. \url{https://doi.org/10.1002/etc.3775}

Hu, X. F., \textbf{Eccles, K. M.}, Chan, H. M. (2017). High selenium exposure lowers the odds ratios for hypertension, stroke, and myocardial infarction associated with mercury exposure among Inuit in Canada. \textit{Environment International}, 102, 200-206. \url{https://doi.org/10.1016/j.envint.2017.03.002}

\textbf{Eccles, K. M.}, Checkley, S., Sjogren, D., Barkema, H. W., Bertazzon, S. (2017). Lessons learned from the 2013 Calgary flood: Assessing risk of drinking water well contamination. \textit{Applied Geography}, 80, 78-85. \url{https://doi.org/10.1016/j.apgeog.2017.02.005}

\textbf{Eccles, K.M.}, Bertazzon, S. (2015). Applications of geographic information systems in public health: A geospatial approach to analyzing MMR immunization uptake in Alberta. \textit{Canadian Journal of Public Health}, 106(6). \url{https://doi.org/10.17269/cjph.106.4981}

Bertazzon, S., Johnson, M., \textbf{Eccles, K.}, Kaplan, G. G. (2015). Accounting for spatial effects in land use regression for urban air pollution modelling. \textit{Spatial and Spatio-temporal Epidemiology}. 14-15, 9–21. \url{https://doi.org/10.1016/j.sste.2015.06.002}

%\end{etaremune}

\vspace*{.1in}
\section{\sc Technical Reports}
Health Canada. (2025). Combined Exposure to Multiple Chemical(Mixture) Risk Assessment (RA): A Quick Guide for Risk Assessors. Ottawa, Canada.

AMAP. (2021). AMAP Assessment 2021: Mercury in the Arctic. Arctic Monitoring and Assessment Programme (AMAP), Tromsø, Norway. 324 pp\\
$^{*}$Contributing author to Chapter 2: Temporal trends of mercury in Arctic media\\
\vspace*{.1in}

\section{\sc Invited Talks}

%\begin{etaremune}[start=9]


\textbf{Eccles K.M.} (2025). Advancing Chemical Mixtures Risk Assessment: Lessons Learned from New Approach Methods and Conputational Modeling. Michigan Society of Toxiclogy Meeting. Ann Arbor, Michigan, USA.

\textbf{Eccles K.M.} (2025). Innovative Approaches for One Health and Chemical Mixtures: Bridging Disciplines for Integrated Solutions. Japanese Society of Tociology. Okinawa, Japan.

\textbf{Eccles K.M.} (2025). Mapping Biology: Innovative Applications of [Geo]spatial Analysis in Toxicology. Seminar. The Broad Institute of MIT and Harvard. Cambridge, Massachusetts, USA.

\textbf{Eccles K.M.} (2025). Bridging Ecosystems and Health: Geospatial Toxicology in the One Health Era. Departmental Seminar. University of Ottawa. Ottawa, Canada.

\textbf{Eccles K.M.} (2024). Unraveling the Complexity: Component-based approaches to quantify the effects of exposure to PFAS Mixtures. Center for PFAS and Cancer (CPAC) Joint Virtual Symposium. Georgetown University. Washington, DC, USA.

\textbf{Eccles K.M.} (2024). Mapping Metal Mixtures: Using Wildlife as Sentinels for Human Health. Society of Toxicology Annual Meeting. Salt Lake City, USA.

\textbf{Eccles K.M.} (2024). Geospatial and Computational Approaches to Support the Risk Assessment of Chemical Mixtures within an AEP-AOP Framework. Society of Toxicology Annual Meeting. Salt Lake City, USA.

\textbf{Eccles K.M.} (2023). From Molecules to Maps: Assessing spatial patterns of contaminant sources, exposures, and health effects on humans and wildlife. Bureau Seminar. Health Canada. Ottawa, Canada.

\textbf{Eccles K.M.} (2022). From Molecules to Maps: Assessing spatial patterns of contaminant sources, exposures, and health effects on humans and wildlife. Department Seminar. Rutgers University. Newark, New Jersey, USA.

\textbf{Eccles K.M.} (2020). From biomarkers to biomes: Relationships between contaminant sources, exposures, and health outcomes. University of Toronto Intersectional Seminar Series. Toronto, Canada.

\textbf{Eccles K.M.} (2020). Humans, wildlife, and the environment: Assessing ecological health. 2nd Annual GeoHealth Network Conference. Toronto, Canada. (Cancelled due to COVID-19)

\textbf{Eccles K.M.},Chan H.M. (2018). Mercury in wild foods and food security: Integrating data (Presentation). Environment and Climate Change Canada (ECCC) Wildlife Division Health Division Annual Meeting. Ottawa, Canada.

\textbf{Eccles K.M.}, Chan H.M. (2018). Modelling the relationship between contaminant sources and exposures in wildlife (Presentation). Environment and Climate Change Canada (ECCC) National Pollution Release Inventory (NPRI) Data Users Workshop. Ottawa, Canada.
%\end{etaremune}

%%%%%%% Conferences %%%%%%%
\vspace*{.1in}
\section{\sc Selected Conference Presentations (12/26)}

%\begin{etaremune}[start=12]
\textbf{Eccles K.M.}, Chan, H.M. (2024). The development and application of methylmercury-to-total mercury ratios for exposure assessment of methylmercury from the consumption of traditional foods (Presentation). International Conference on Mercury as a Global Pollutant, Cape Town, South Africa.

\textbf{Eccles K.M.}, Blais, A., Zhang, G., Girgis, A., Pelletier, G., Aranda-Rodriguez, R., Tayabali, A. (2024). Putting the 3Rs into action: a coupled \textit{in silico}, \textit{in vitro}, and \textit{in vivo} study to quantify immunological effects of per- and poly-fluroakyl substances (PFAS) (Poster). Society of Toxicology, Salt Lake City, USA.

\textbf{Eccles K.M.}, Karmaus, A. L., Kleinstreuer, N. C., Parham, F., Rider, C. V., Messier, K. P. (2023). Mapping a Path to Disease: Quantifying the risk of exposure to environmental chemical mixtures via a common molecular target using a geospatial modeling approach (Presentation). Society of Toxicology, Nashville, USA.\\
$^{*}$1st place winner of best postdoctoral abstract for the SOT Mixtures specialty section

\textbf{Eccles K.M.}, Rider, C. V., Messier, K. P. (2022). Geospatial Risk Assessment Using High-Throughput Screening Assays To Quantify Potential Adverse Effects From Exposure To Chemical Mixtures (Presentation). Society of Environmental Toxicology and Chemistry, Pittsburgh, USA.

\textbf{Eccles K.M.}, Karmaus, A. L., Kleinstreuer, N. C., Parham, F., Rider, C. V., Wambaugh, J. F., Messier, K. P. (2022). A geospatial modeling approach to quantifying the risk of exposure to environmental chemical mixtures via a common molecular target (Poster). North Carolina Society of Toxicology, Durham, USA.\\
$^{*}$1st place winner of best postdoctoral poster and presentation

\textbf{Eccles K.M.}, Messier, K.P, (2021). Geospatial Risk Characterization Mapping of Chemical Mixtures Through Connections to Toxicological Adverse Outcome Pathways (Presentation). American Geophysical Union, New Orleans, USA.

\textbf{Eccles K.M.}, Kleinstreuer, N.C., Wambaugh, J.F., Messier, K.P, (2021). A geospatial modeling approach to quantifying risk of exposure to environmental chemical mixtures via a common molecular initiating event (Poster). International Society of Environmental Epidemiology, New York, USA.

\textbf{Eccles K.M.}, Clackett A., Ghotra, A., Majeed, I., Lehnherr, I., Porter, T. (2020). Developing a network of historical atmospheric mercury trends using tree-rings in northern Canada (Presentation).  Society of Environmental Toxicology and Chemistry, Fort Worth, USA.

\textbf{Eccles K.M.}, Clackett A., Ghotra, A., Majeed, I., Lehnherr, I., Porter, T. (2019). Assessing variability of atmospheric mercury (Hg$^{0}$) trends using tree-rings in northern Canada (Presentation). Society of Environmental Toxicology and Chemistry. Toronto, Canada.

\textbf{Eccles K.M.}, Thomas P.J., Chan H.M. (2019). Wildlife as a surrogate indicator for impacts of mercury on ecosystem health (Presentation). International Conference on Mercury as a Global Pollutant. Krakow, Poland.

\textbf{Eccles K.M.}, Thomas P.J., Chan H.M. (2018). Wildlife as a surrogate indicator for impacts of mercury on ecosystem health (Presentation). Society of Environmental Toxicology and Chemistry. Sacramento, USA.

\textbf{Eccles K.M.}, Thomas P.J., Chan H.M. (2018). Evaluating the co-dispersion of mercury sources and wildlife exposures in the Athabasca Oil Sands region (Presentation). Society of Environmental Toxicology and Chemistry. Sacramento, USA.

%\end{etaremune}

%%%%%%% Media %%%%%%%
\vspace*{.1in}
\section{\sc Media}
\textbf{SOT TV 2024}\\
Innovation Uncaged: from lab to screen in chemical hazard assessment \href{https://www.youtube.com/watch?v=6Pg7DvoHgP0}{[YouTube Link]}

The Next Frontier in Toxicology: Computational and Geospatial Methods in Toxicology Research \href{https://www.youtube.com/watch?v=-vlSMeWfeKs\&t=939s}{[YouTube Link to full video]}
\href{https://www.youtube.com/watch?v=vgu6d1uT8K4}{[YouTube Link to segment]}

%%%%%%% Teaching %%%%%%%

\vspace*{.1in}
\section{\sc Teaching Experience}
\textbf{Primary Instructor}\\
Lecture and lab: High-throughput screening (ToxCast and Tox21 program) \hfill {\textbf{Winter 2025}}\\
and high-content data sources (3 hours) \hfill {\textbf{Winter 2024}}\\
BIM4103 Selected Topics in Biomedical Science, University of Ottawa\\
Teaching Material: \url{https://github.com/kristineccles/BIM4103-HTS-Dose-Response}

Graduate Level Short Course: Introduction to R in Open-Source Methods (6 hours) \hfill {\textbf{Winter 2020}}\\
Department of Geography, Geomatics and Environment, University of Toronto \hfill {\textbf{Fall 2020}}
\\Teaching Material: \url{https://github.com/kristineccles/Introduction_to_R}

Geographic Information Systems \hfill {\textbf{Spring 2020}}\\
Department of Geography, Geomatics and Environment, University of Toronto

Introduction to Quantitative Methods
 \hfill {\textbf{Winter 2018}}\\
Department of Geography and Environmental Studies, Carleton University\\
Teaching Material: \url{https://github.com/kristineccles/introduction_to_stats}

Mapping and Modelling the Real World: Introduction to GIS \hfill {\textbf{May 2017}}\\
Enrichment Mini-Course, University of Ottawa

Introduction to Geomatics
\hfill {\textbf{Fall 2016}}\\
Department of Geography, Environment and Geomatics, University of Ottawa

\vspace*{.1in}

%%%%%%% Awards %%%%%%%
\section{\sc Competitive Awards}

Assistant Deputy Minister Awards for Excellence - Science (2025)
\hfill {\textbf{Recognition}}\\
Society of Toxicology (SOT) Mixtures Specialty Section\\
\tab Best Postdoctoral Abstract (2023)
\hfill {\textbf{\$1000}}\\
Society of Toxicology (SOT) Biological Modeling Specialty Section\\
\tab Andersen-Clewell Trainee Award - 2nd Place (2023)
\hfill {\textbf{Recognition}}\\
NIEHS Paper of the Year (2022)
\hfill {\textbf{Recognition}}\\
North Carolina Society of Toxicology (NCSOT)\\
\tab Best Postdoctoral Poster and Presentation (2022)
\hfill {\textbf{\$300}}\\
SETAC Travel Award (2022)
\hfill {\textbf{\$1050}}\\
University of Toronto Postdoctoral Award (2019-2020)
\hfill {\textbf{\$45,000}}\\
NSERC CREATE-REACT (2016 - 2018)
\hfill {\textbf{\$20,000}}\\
NSERC CREATE-REACT Travel Award (2018)
\hfill {\textbf{\$5,000}}\\
University of Ottawa Excellence Scholarship (2016 - 2017)
\hfill {\textbf{\$8,200}}\\
Queen Elizabeth II Graduate Scholarship in Science and Technology (2016 - 2017)
\hfill {\textbf{\$15,000}}\\
University of Ottawa Entrance Scholarship (2014 - 2018)
\hfill {\textbf{\$38,000}}\\

\vspace*{.1in}

%%%%%%% Leadership and Service %%%%%%%
\section{\sc Leadership and Service}
{\bf Board Member}\\
{Vice-President - Society of Toxicology Lake Ontario Regional Chapter} \hfill {\bf 2024 - Present}\\
{Junior Councillor - Society of Toxicology Mixtures Specialty Section} \hfill {\bf 2025 - Present}\\
{Postdoctoral Representative - Society of Toxicology Mixtures Specialty Section} \hfill {\bf 2023 - 2024}\\


{\bf Conference Sessions and Workshops Organized}

International Conference on Mercury as a Global Pollutant, Cape Town, South Africa \hfill {\bf July 2024}\\
Workshop: Bio-monitoring to achieve goals in Minamata Convention

Society of Toxicology, Salt Lake City, USA \hfill {\bf  March 2024}\\
Workshop Session: Integrating Aggregate Exposure Pathways and Adverse Outcome Pathways for Comprehensive Risk Assessment of Chemical Mixtures

Society of Environmental Toxicology and Chemistry, Fort Worth, USA \hfill {\bf  Nov 2020}\\
On Demand Session: Mercury emissions, transport, and transformation in a changing environment\\
Live Discussion: Pathways between Hg sources and exposures in a changing world

Workshop: Introduction to R
Course Material: \url{https://github.com/kristineccles/setac_intro_to_r_2020}

International Conference on Mercury as a Global Pollutant, Krakow, Poland \hfill {\bf Sept 2019}\\
Workshop: Latest Advances in Wildlife Biomonitoring

{\bf Expert Working Group Member}\\
Arctic Monitoring Assessment Program (AMAP)
\hfill {\bf  June 2019- Sept 2020}\\
Mercury Expert Working Group

Oil Sands Monitoring Integration Workshop Series
\hfill {\bf  Jan 2019}\\
External Expert for Geospatial Analysis and Mercury

\vspace*{.1in}

\section{\sc Additional Training}
Training in the Responsible Conduct of Research, National Institutes of Health \hfill {\bf  Fall 2021}\\
Teaching Fundamentals Certificate, University of Toronto
\hfill {\bf  Winter 2020}\\
Machine Learning, University of Toronto
\hfill {\bf  Fall 2019}

\vspace*{.1in}

\section{\sc Languages}

English - Native Language, French - Intermediate\\
R - Advanced, Python - Intermediate, LaTeX- Intermediate

\vspace*{.1in}

\section{\sc Professional Memberships}
Society of Toxicology (SOT) 2021 - Present

\end{resume}
\end{document}




